---
title: "Function: random_recipe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function: random_recipe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The `random_recipe` function in the `Mealsuggestor` package is designed to select a random recipe from the dataset. This function is perfect for users who want a bit of surprise and are open to trying something new without specific preferences in mind.

## Parameters

- `data`: A data frame containing the recipes.

## Returns

This function returns a single randomly selected recipe from the provided dataset.

## Example Usage

The following example shows how to use the `random_recipe` function to randomly select a recipe from a dataset:

```{r random-recipe-example, eval=FALSE}
library(Mealsuggestor)

# Example dataset 

randomly_selected_recipe <- random_recipe(data = recipes)

# Display the randomly selected recipe
print(randomly_selected_recipe)
