---
title: "Function: sort_recipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function: sort_recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Overview

The `sort_recipes` function in the `Mealsuggestor` package enables users to sort recipes based on a specified criterion, such as rating or preparation time. This functionality is essential for organizing recipes according to specific needs or preferences.

## Parameters

- `data`: A data frame containing the recipes.
- `sort_by`: The column name to sort by (e.g., "rating", "prep_time").
- `ascending`:  if `TRUE`, sorts in ascending order, else in descending order. Default is `TRUE`.

## Returns

This function returns a sorted data frame of recipes based on the specified criteria.

## Example Usage

The following example demonstrates how to use the `sort_recipes` function to sort recipes by rating in descending order:

```{r sort-recipes-example, eval=FALSE}
library(Mealsuggestor)

sorted_recipes <- sort_recipes(data = recipes, sort_by = "rating", ascending = FALSE)

# Display the sorted recipes
print(sorted_recipes)

```







